Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2025-05-14 paper.qmd
Found the way to arrange images

highd_error_2d_mnist <- error_df |>
  ggplot(aes(x = tSNE1,
             y = tSNE2,
             colour = sqrt_row_wise_tot_error)) +
  geom_point(alpha=0.2) +
  scale_colour_continuous_sequential(palette = "YlOrRd", n_interp = 20) +
  geom_rect(aes(xmin = 0.82, xmax = 0.92, ymin = 0.38, ymax = 0.58),
               fill = "transparent", color = "#000000", linewidth = 1) +
  geom_rect(aes(xmin = 0.9, xmax = 1, ymin = 1.25, ymax = 1.45),
               fill = "transparent", color = "#375cb1", linewidth = 1)  +
  geom_rect(aes(xmin = 0.35, xmax = 0.45, ymin = 0.55, ymax = 0.7),
               fill = "transparent", color = "#004616", linewidth = 1)  +
  geom_rect(aes(xmin = 0.7, xmax = 0.8, ymin = 0.25, ymax = 0.4),
               fill = "transparent", color = "#4c389a", linewidth = 1) +
  theme(legend.position = "none",
        aspect.ratio = 1,
        plot.margin = margin(0, 0, 0, 0))
```

@@

img_right_top <- c(868, 1465, 1787)

@@

img_middle <- c(130, 2091, 7795)

@@

img_right_bottom <- c(2035, 7708, 7710)

@@

img_error_outside <- c(999, 3650, 4916)

@@

##### inside
img_error_inside <- c(3179, 7363, 7650) #, 5241, 5173, 6981, 7228, 6673, 4636

@@

imge_error_sample_inside <- plot_digit_img(
  pixels_gathered_inside, palette = "Oranges", title_text = "e", ncol = 3)

@@

```{r}
#| label: fig-model-error-mnist
#| fig-cap: "The $10\\text{-}D$ model error in \\gD{} layout of the MNIST digit 1 data shows a pattern. Most low model errors are distributed along the big non-linear cluster, while most large model errors are distributed along the small cluster. The images associated with large model errors shows different patterns of digit 1, some inside (e) the non-linear structure and others outside (d). Along the non-linear cluster, the angle of digit 1 changes (a-c)."
#| fig-pos: H
#| fig-width: 12
#| fig-height: 6
#| out-width: 90%

# Define your current layout
# top_layout <- right_top_img / middle_img / right_bottom_img / imge_error_sample_outside

top_layout <- wrap_plots(
  right_top_img,
  middle_img,
  right_bottom_img,
  imge_error_sample_outside,
  ncol = 1,
  heights = c(1, 1, 1, 1)
) + plot_layout() + plot_annotation(theme = theme(plot.margin = margin(0, 0, 0, 0)))

# Combine with main plot
full_layout <- highd_error_2d_mnist + top_layout +
  plot_layout(widths = c(1, 1)) +
  plot_annotation(theme = theme(plot.margin = margin(0, 0, 0, 0)))

# Add the new full-width bottom row
final_layout <- full_layout / imge_error_sample_inside + plot_layout(heights = c(1, 0.2))

# Display the final combined plot
#final_layout
full_layout

# /imge_error_sample_inside + plot_layout(widths = c(1, 1), 
#                                                    heights = c(1, 0.2))
```

>>>>

highd_error_2d_mnist <- error_df |>
  ggplot(aes(x = tSNE1,
             y = tSNE2,
             colour = sqrt_row_wise_tot_error)) +
  geom_point(alpha=0.2) +
  scale_colour_continuous_sequential(palette = "YlOrRd", n_interp = 20) +
  geom_rect(aes(xmin = 0.82, xmax = 0.92, ymin = 0.38, ymax = 0.58),
               fill = "transparent", color = "#000000", linewidth = 1) +
  geom_rect(aes(xmin = 0.9, xmax = 1, ymin = 1.25, ymax = 1.45),
               fill = "transparent", color = "#375cb1", linewidth = 1)  +
  geom_rect(aes(xmin = 0.35, xmax = 0.45, ymin = 0.55, ymax = 0.7),
               fill = "transparent", color = "#004616", linewidth = 1)  +
  geom_rect(aes(xmin = 0.7, xmax = 0.8, ymin = 0.25, ymax = 0.4),
               fill = "transparent", color = "#4c389a", linewidth = 1) +
  theme(legend.position = "none",
        aspect.ratio = 1,
        plot.margin = margin(0, 0, 0, 0),
        panel.spacing = unit(0, "pt"),
        axis.ticks.length = unit(0, "pt"),
        strip.text = element_blank(),   # Optional, if you're using facets
        axis.title = element_blank()   # Optional
        )
```

@@

img_right_top <- c(868, 1465, 1787, 1788, 1789)

@@

img_middle <- c(130, 2091, 7795, 7796, 7797)

@@

img_right_bottom <- c(2035, 7708, 7710, 7711, 7712)

@@

img_error_outside <- c(999, 3650, 4916, 4917, 4918)

@@

##### inside
img_error_inside <- c(5173, 6981, 7228, 6673, 3179) #, 6673, 3179, 7363, 7650, 5241, 4636

@@

imge_error_sample_inside <- plot_digit_img(
  pixels_gathered_inside, palette = "Oranges", title_text = "e")

@@

```{r}
#| label: fig-model-error-mnist
#| fig-cap: "The $10\\text{-}D$ model error in \\gD{} layout of the MNIST digit 1 data shows a pattern. Most low model errors are distributed along the big non-linear cluster, while most large model errors are distributed along the small cluster. The images associated with large model errors shows different patterns of digit 1, some inside (e) the non-linear structure and others outside (d). Along the non-linear cluster, the angle of digit 1 changes (a-c)."
#| fig-pos: H
#| fig-width: 10
#| fig-height: 10
#| out-width: 100%

# Define your current layout
top_layout <- right_top_img + middle_img + right_bottom_img + imge_error_sample_outside + imge_error_sample_inside + plot_layout(nrow = 5)

final_layout <- wrap_plots(highd_error_2d_mnist, top_layout)

final_layout
```
